Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2015-02-24 Paper.tex
message call to account with no code
add identity function

As can be seen, there are three exceptions to the usage of the general execution framework $\Xi$ for evaluation of the message call: these are three so-called `precompiled' contracts, meant as a preliminary piece of architecture that may later become \textit{native extensions}. The three contracts in addresses 1, 2 and 3 execute the elliptic curve public key recovery function, the SHA2 256-bit hash scheme and the RIPEMD 160-bit hash scheme respectively.

>>>>

As can be seen, there are four exceptions to the usage of the general execution framework $\Xi$ for evaluation of the message call: these are four so-called `precompiled' contracts, meant as a preliminary piece of architecture that may later become \textit{native extensions}. The four contracts in addresses 1, 2, 3 and 4 execute the elliptic curve public key recovery function, the SHA2 256-bit hash scheme, the RIPEMD 160-bit hash scheme and the identity function respectively.
